---
title: "Business Health"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(gt)
library(blastula)
library(glue)

source("health_kpis.R")
source("health_thresholds.R")
```

```{r data, include=FALSE}
health_kpis_recent <- get_health_kpis(n = 10)

# Get the KPIs for the most recent day in a list
one_day_kpis <-
  health_kpis_recent %>%
  select(dau, dac, dac_dau, new_users, churn_users, daily_revenue) %>%
  head(1) %>% as.list()

# Compare these KPIs against the thresholds and
# determine if there are any exceedances (TRUE/FALSE)
exceedances <-
  list(
    dau = one_day_kpis$dau < health_thresholds$dau,
    dac = one_day_kpis$dac < health_thresholds$dac,
    dac_dau = one_day_kpis$dac_dau < health_thresholds$dac_dau,
    new_users = one_day_kpis$new_users < health_thresholds$new_users,
    churn_users = one_day_kpis$churn_users > health_thresholds$churn_users,
    daily_revenue = one_day_kpis$daily_revenue < health_thresholds$daily_revenue
  )

# Get the total number of exceedances
total_exceed <- exceedances %>% unlist() %>% sum()

# Get the KPI names for the exceedances
names_exceed <- unlist(exceedances)[unlist(exceedances)] %>% names()
```

## Summary of Business Health

The following table shows our business health KPIs. Each row represents a daily view of the KPIs that determine the success of our product. These are DAU (*Daily Active Users*), DAC (*Daily Active Customers*), the ratio DAC/DAU, our daily New Users and Churned Users, and, our Daily Revenue. If any KPIs are problematic, their values are shaded in light red.

```{r business_health_gt, echo=FALSE}

gt_health <-
  health_kpis_recent %>%
  add_threshold_columns(health_thresholds) %>%
  gt(rowname_col = "date", groupname_col = "week") %>%
  tab_header(
    title = "Daily Health Check for Product KPIs",
    subtitle = "Last 10 days of KPIs shown for Product (weekend in gray)"
  ) %>%
  cols_label(
    date = "Date", dau = "DAU", dac = "DAC", dac_dau = "DAC/DAU",
    new_users = "New", churn_users = "Churned", daily_revenue = "Daily Revenue"
  ) %>%
  highlight_exceedances(health_thresholds) %>%
  highlight_weekends() %>%
  cols_hide(columns = vars(wday)) %>%
  cols_align(align = "right", everything()) %>%
  fmt_number(columns = vars(dau, dac, new_users), suffixing = TRUE, decimals = 1) %>%
  fmt_currency(columns = vars(daily_revenue), currency = "USD", decimals = 0) %>%
  tab_options(table.width = px(740), data_row.padding = px(2.5)) %>%
  cols_width(everything() ~ px(740 / 7)) %>%
  opt_all_caps()

gt_health
```

## Daily Users Chart

The following time-series plot gives us a picture of how our user-based KPIs have been performing over the last 30 days.

```{r ggplot_users, fig.align="center", echo=FALSE}

get_health_kpis(n = 30) %>%
  select(date, dau, dac, new_users, churn_users) %>%
  pivot_longer(
    cols = dau:churn_users,
    names_to = "type",
    values_to = "n"
  ) %>%
  mutate(type = type %>% fct_relevel(c("dau", "dac", "new_users", "churn_users"))) %>%
  ggplot() +
  geom_line(aes(x = date, y = n, color = type)) +
  scale_y_log10(
    labels = scales::comma_format(),
    breaks = c(10, 1e2, 1e3, 1e4, 1e5, 1e6, 1e7)) +
  labs(
    title = "Daily Numbers for Users of our Product",
    subtitle = "Split between DAU, DAC, new users, and churning users\n",
    x = "", y = "Users",
    color = "KPI"
  ) +
  theme_minimal() +
  theme(
    plot.title.position = "plot",
    plot.caption.position =  "plot",
    legend.position = "top"
  )
```

## Daily Revenue Chart

The following time-series plot (as before, showing the last 30 days) gives us a picture of how our daily revenue has been changing over time.

```{r ggplot_revenue, fig.align="center", echo=FALSE}

get_health_kpis(n = 30) %>%
  select(date, daily_revenue) %>%
  ggplot(aes(x = date, y = daily_revenue)) +
  geom_line(color = "forestgreen", size = 1) +
  geom_point(size = 2, shape = 21, color = "forestgreen", fill = "white", stroke = 1) +
  scale_y_continuous(labels = scales::dollar_format(), limits = c(0, NA)) +
  labs(
    title = "Daily Revenue for our Product",
    subtitle = "Revenue amounts in USD and adjusted for refunds\n",
    x = "", y = ""
  ) +
  theme_minimal() +
  theme(
    plot.title.position = "plot",
    plot.caption.position =  "plot"
  )
```

This is a raw table of the recent KPI data (last 10 days).

```{r health_kpis, echo=FALSE}
health_kpis_recent
```


```{r health_kpis_recent_csv, echo=FALSE}
health_kpis_recent %>% readr::write_csv("health_kpis_recent.csv")
```


```{r connect_email_setup, echo=FALSE}
if (total_exceed > 0) {
  render_connect_email(input = "business_health_email.Rmd") %>%
    attach_connect_email(
      subject = glue(
        "One or more KPIs ({total_exceed}) broke thresholds: \\
        {paste(names_exceed, collapse = ', ')}"
      ),
      attachments = "health_kpis_recent.csv"
    )
} else {
  suppress_scheduled_email() 
}
```
